Retrofitting Effect Handlers onto OCaml

### 2020-11-06 retro-concurrency.tex
More evaluation

>>>>

Next we look at benchmarks that utilize non-local control flow. First, we
quantify the overhead individual operations in effect handling. Consider the
following annotated code:
\begin{lstlisting}
effect E : unit
(* a *) match (* b *) perform E (* d *) with
| v -> (* e *) v
| effect E k -> (* c *) continue k ()
\end{lstlisting}
The sequence |a-b| involves allocating a new fiber and switching to it. |b-c|
is performing the effect and handling it. |c-d| is resuming the continuation.
|d-e| is returning from the fiber with a value and freeing the fiber. We
measured the time taken to execute these sequences using |perf| support for
cycle-accurate tracing on modern Intel processors. We executed 10 iterations of
the code, ignoring 3 warm-up runs. We observed that the sequences
|a-b|, |b-c|, |c-d| and |d-e| took 48ns, 10ns, 13ns and 19ns, respectively. For
reference, the idle memory latency for the local NUMA node is 93.2ns.
